Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-04-08 manuscript/cpcrw_manuscript.Rmd
Added WFPS calculation and Q10s normalized by it
See issue #30

```{r coredata, echo=FALSE}
bd <- with(coredata, SoilDryMass_g / CoreVolume_cm3)
schist <- with(coredata, NonsoilMassLarge_g / (NonsoilMassLarge_g + SoilDryMass_g)) * 100
sdm <- coredata$SoilDryMass_g
```

@@

Gravimetric water content was `r pn(gwcbegin$mean, 2)` ± `r pn(gwcbegin$sd, 2)` (min `r pn(gwcbegin$min, 2)`, max `r pn(gwcbegin$max, 2)`) at the beginning of the incubation (**Figure 1**). "Field moisture" cores were on average unchanged (`r pn(gwcendmean["Field moisture"], 2)` ± `r pn(gwcendsd["Field moisture"], 2)`) at the end of the incubation, but both the drought treatments, which did not differ from each other in their effect on gravimetric water content (P = `r pn(p_trt_wc, 3)`), had declined to `r pn(gwcendmean["Drought"], 2)` ±  `r pn(gwcendsd["Drought"], 2)`. Volumetric water content values ranged from `r pn(vwcbegin$mean, 2)` ± `r pn(vwcbegin$sd, 2)` (min `r pn(vwcbegin$min, 2)`, max `r pn(vwcbegin$max, 2)`) at the beginning of the experiment to `r pn(vwcend$mean, 2)` ± `r pn(vwcend$sd, 2)` (min `r pn(vwcend$min, 2)`, max `r pn(vwcend$max, 2)`) at the end.

@@

The cumulative flux numbers above result in CH~4~ temperature sensitivity (Q~10~) values of `r pn(q10_cumulative["Field moisture", "CH4"], 1)` and `r pn(q10_cumulative["Drought", "CH4"], 1)` for the field moisture and drought treatments, respectively; the corresponding Q~10~ values  based on cumulative CO~2~ were `r pn(q10_cumulative["Field moisture", "CO2"], 1)` and `r pn(q10_cumulative["Drought", "CO2"], 1)`.

@@

>>>>

```{r coredata, echo=FALSE}
bd <- with(coredata, SoilDryMass_g / SoilVolume_cm3)
schist <- with(coredata, NonsoilMassLarge_g / (NonsoilMassLarge_g + SoilDryMass_g)) * 100
sdm <- coredata$SoilDryMass_g
```

@@

Gravimetric water content was `r pn(gwcbegin$mean, 2)` ± `r pn(gwcbegin$sd, 2)` (min `r pn(gwcbegin$min, 2)`, max `r pn(gwcbegin$max, 2)`) at the beginning of the incubation (**Figure 1**). "Field moisture" cores were on average unchanged (`r pn(gwcendmean["Field moisture"], 2)` ± `r pn(gwcendsd["Field moisture"], 2)`) at the end of the incubation, but both the drought treatments, which did not differ from each other in their effect on gravimetric water content (P = `r pn(p_trt_wc, 3)`), had declined to `r pn(gwcendmean["Drought"], 2)` ±  `r pn(gwcendsd["Drought"], 2)`. Volumetric water content values ranged from `r pn(vwcbegin$mean, 2)` ± `r pn(vwcbegin$sd, 2)` (min `r pn(vwcbegin$min, 2)`, max `r pn(vwcbegin$max, 2)`) at the beginning of the experiment to `r pn(vwcend$mean, 2)` ± `r pn(vwcend$sd, 2)` (min `r pn(vwcend$min, 2)`, max `r pn(vwcend$max, 2)`) at the end. Water filled pore space, assuming a particle density of `r PARTICLE_DENSITY` g cm^-3^, was `r pn(min(fluxdata$WFPS_percent), 0)`-`r pn(max(fluxdata$WFPS_percent), 0)`%.

@@

The cumulative flux numbers above result in CH~4~ temperature sensitivity (Q~10~) values of `r pn(Q10_cumulative["Field moisture", "CH4"], 1)` and `r pn(Q10_cumulative["Drought", "CH4"], 1)` for the field moisture and drought treatments, respectively; the corresponding Q~10~ values  based on cumulative CO~2~ were `r pn(Q10_cumulative["Field moisture", "CO2"], 1)` and `r pn(Q10_cumulative["Drought", "CO2"], 1)`. Computing Q~10~s based on fluxes normalized by water filled pore space decreased these values slightly: to `r pn(wfpsQ10_cumulative["Field moisture", "CH4"], 1)` and `r pn(wfpsQ10_cumulative["Drought", "CH4"], 1)` for CH~4~, respectively, and `r pn(wfpsQ10_cumulative["Field moisture", "CO2"], 1)` and `r pn(wfpsQ10_cumulative["Drought", "CO2"], 1)` for CO~2~.

@@

Modeling results highly dependent on water content of soils after permafrost degradation.
